Growth of the South African Economy:\\An Empirical Evaluation

### 2014-08-11 Articles/Article_EcolEcon_2014/Paper2.Rnw
Articles now use setwd("../..").

<<data, include=FALSE, eval=TRUE>>=
# Load historical data
historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package
# Load coefficients from all models in one large data frame
REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs")
IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs")
Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs")
AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
AllCoeffs$Source <- as.factor(replace(AllCoeffs$Source, which(AllCoeffs$Source=="REXS1960"), "REXS"))
AllCoeffs$Source <- relevelFactor(AllCoeffs$Source, levs = c("REXS", "IST", "Leeds"))
AllCoeffs$energy <- relevelFactor(AllCoeffs$energy, levs = energyLevels)
# Load fitted data from all models in one large data frame
REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted")
IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted")
Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted")
AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)
AllFitted$Source <- replace(AllFitted$Source, which(AllFitted$Source=="REXS1960"), "REXS")
AllFitted$Source <- relevelFactor(as.factor(AllFitted$Source), levs = c("REXS", "IST", "Leeds"))
AllFitted$energy <- relevelFactor(AllFitted$energy, levs=energyLevels)
@

>>>>

<<data, include=FALSE, eval=TRUE>>=
# Load historical data
historicalData <- rbind.fill(REXS1960, IST, Leeds) # From the EconData package

# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
# This is the same directory from which the RStudio project runs.
# Setting this working directory eliminates the need to use dir="../.." in the 
# loadPostPorcessedData function calls below.
setwd(file.path("..", ".."))

# Load coefficients from all models in one large data frame
REXS1960_Coeffs <- loadPostProcessedData(Source = "REXS1960", kind = "coeffs")
IST_Coeffs <- loadPostProcessedData(Source = "IST", kind = "coeffs")
Leeds_Coeffs <- loadPostProcessedData(Source = "Leeds", kind = "coeffs")
AllCoeffs <- rbind(REXS1960_Coeffs, IST_Coeffs, Leeds_Coeffs)
AllCoeffs$Source <- as.factor(replace(AllCoeffs$Source, which(AllCoeffs$Source=="REXS1960"), "REXS"))
AllCoeffs$Source <- relevelFactor(AllCoeffs$Source, levs = c("REXS", "IST", "Leeds"))
AllCoeffs$energy <- relevelFactor(AllCoeffs$energy, levs = energyLevels)
# Load fitted data from all models in one large data frame
REXS1960_Fitted <- loadPostProcessedData(Source = "REXS1960", kind = "fitted")
IST_Fitted <- loadPostProcessedData(Source = "IST", kind = "fitted")
Leeds_Fitted <- loadPostProcessedData(Source = "Leeds", kind = "fitted")
AllFitted <- rbind(REXS1960_Fitted, IST_Fitted, Leeds_Fitted)
AllFitted$Source <- replace(AllFitted$Source, which(AllFitted$Source=="REXS1960"), "REXS")
AllFitted$Source <- relevelFactor(as.factor(AllFitted$Source), levs = c("REXS", "IST", "Leeds"))
AllFitted$energy <- relevelFactor(AllFitted$energy, levs=energyLevels)
@

### 2014-08-11 Articles/Article_EnerEcon_2014/EconGrowth3.Rnw
Articles now use setwd("../..").

<<data>>=
# Load historical data
historicalData <- Calvin # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
@

>>>>

<<data>>=
# Load historical data
historicalData <- Calvin # From the EconData package

# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
# This is the same directory from which the RStudio project runs.
# Setting this working directory eliminates the need to use dir="../.." in the 
# loadPostPorcessedData function calls below.
setwd(file.path("..", ".."))

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
@

### 2014-08-11 Articles/Article_Heun_Warr_2014/EcolEcon_HeunWarr.Rnw
Articles now use setwd("../..").

<<data, include=FALSE, eval=TRUE>>=
# Load historical data
historicalData <- REXS # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "REXS", kind = "coeffs")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "REXS", kind = "fitted")
# Load the original models.
oModels <- loadPostProcessedData(Source = "REXS", kind = "models")
@

>>>>

<<data, include=FALSE, eval=TRUE>>=
# Load historical data
historicalData <- REXS # From the EconData package

# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
# This is the same directory from which the RStudio project runs.
# Setting this working directory eliminates the need to use dir="../.." in the 
# loadPostPorcessedData function calls below.
setwd(file.path("..", ".."))

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "REXS", kind = "coeffs")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "REXS", kind = "fitted")
# Load the original models.
oModels <- loadPostProcessedData(Source = "REXS", kind = "models")
@

### 2014-08-11 Articles/Article_JAE_2014/ZAGrowth_JAE.Rnw
Articles now use setwd("../..").

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs", dir = "../../data_postprocessed")
coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted", dir = "../../data_postprocessed")
fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models", dir = "../../data_postprocessed")
oModels_ZA <- oModels$Calvin$ZA
@

>>>>

# Set working directory to the top level of the repository: Econ-Growt-R-Analysis
# This is the same directory from which the RStudio project runs.
# Setting this working directory eliminates the need to use dir="../.." in the 
# loadPostPorcessedData function calls below.
setwd(file.path("..", ".."))

# Load coefficients from all models in one large data frame
coeffs_df <- loadPostProcessedData(Source = "Calvin", kind = "coeffs")
coeffs_df_ZA <- subset(coeffs_df, subset=country=="ZA")
# Load fitted data from all models in one large data frame
fitted_df <- loadPostProcessedData(Source = "Calvin", kind = "fitted")
fitted_df_ZA <- subset(fitted_df, subset=Country=="ZA")
# Load the original models.
oModels <- loadPostProcessedData(Source = "Calvin", kind = "models")
oModels_ZA <- oModels$Calvin$ZA
@
